Enhancing the sales prediction of newly published books by means of computational intelligence methods

### 2016-03-14 paper.tex
A very extensive rearrangement of the problem description and results section should be done.
Please @amorag revise comments and so on.

Thus, in this research five forecasting methods, based on the literature 
review in the introduction 
\cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, have been used. 
Well known forecasting methods implemented in the Weka tool
\cite{Hall2009,Witten2011} have been chosen, as these methods are
widely known, and could be very helpful for practitioners to reproduce
experiments and even to solve similar sales prediction problems using
these methods.

Specifically, the following forecasting methods are proposed:
\begin{itemize}

@@

@@

In most of data mining and machine algorithms, the values of some parameters could have a high influence on its performance. In our experiments, the best value of $k$ in the $k$-nearest neighbour was empirically found at $k=3$. For SVM, the widely used Radial Basis Function (RBF) kernel is selected. As reported in several studies, RBF kernel has a reliable performance and can analyse higher dimensional data \cite{yu2004ec,chao2015construction,huang2006ga}. Two important parameters should be tuned in SVM: the Cost $(C)$ and $(\gamma)$ of the RBF kernel. We apply grid search which is the most common approach to find $C$ and $\gamma$. The best performance of SVM was found at $C=200$ and Gamma $\gamma = 0.01$. For MLP, we apply it with one hidden layer since it was proven in the literature that an MLP with one hidden layer can approximate any continuous or discontinuous function \cite{hornik1989multilayer,mirjalili2014let}. However, there is no rule of thumb on selecting the best number of neurons in the hidden layer. One suggested method that is followed in this work is to set the number of neurons in the hidden layer to $2 \times I + 1$ where $I$ is the number of inputs in the dataset \cite{wdaa2008differential,mirjalili2014let,mirjalili2015effective}.

All experiments are performed using 10-folds cross validation. The dataset is partitioned into 10 parts where the training process is carried out on 9 parts then the resulted model is tested on the left 10th part. This process is repeated 10 times, each time the model is trained using different 9 parts. At the end of the process the 10 evaluation results on the testing parts are averaged.

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.60]{freq_sales.eps}
\end{center}
\caption{Number of books in each category.}
\label{fig:count}
\end{figure*}

@@

In Figure \ref{fig:Umatrix} we label the U-matrix with the total-sales
categories. It can be clearly shown that the SOM algorithm has
successfully clustered the labels of the Total Sales into clear
identified regions. In the top of the U-matrix the VL category is
located. The L category appears in the middle of the matrix. Most of
the M category appears in bottom-right corner while the H and VH
categories are concentrated in the bottom-left corner.
By inspecting \texttt{num\_reprints}, \texttt{gifts},
\texttt{distrib\_novelty}, \texttt{tot\_points\_sale},
\texttt{tot\_points\_sale\_1st\_year} and \texttt{print\_run}
components, it can be noticed that they have the highest similarity to
the clusters shown in the U-matrix. Based on this analysis, those
features will be selected for the next stage.

@@

\begin{figure*}[http] 
\begin{center} 
\begin{tabular}{ccc}
\includegraphics[scale=0.22]{m5p.eps}  &
\includegraphics[scale=0.22]{lr.eps}   &
\includegraphics[scale=0.22]{svm.eps}  \\
M5P & LR & SVM 
\end{tabular}
\begin{tabular}{cc}
\includegraphics[scale=0.22]{knn.eps}  &
\includegraphics[scale=0.22]{mlp.eps}  \\
k-NN & MLP
\end{tabular}
\end{center} 
\caption{Actual VS predicted sales for M5P, LR, SVM, k-NN, MLP models.}
\label{conv2}
\end{figure*}

>>>>

Thus, in this research five forecasting methods, based on the literature 
review in the introduction 
\cite{Madsen2008,ChingChin2010,Thomassey2012,Xia2012,SThomassey2014}, have been used. 
Well known forecasting methods implemented in the Weka tool
\cite{Hall2009,Witten2011} have been chosen, as these methods are
widely known, and could be very helpful for practitioners to reproduce
experiments and even to solve similar sales prediction problems using
these methods. % Why these and not others? Exploratory data analysis?
               % - JJ

Specifically, the following forecasting methods are proposed: % Proposed why? - JJ
\begin{itemize}

@@

%An intro should go here - JJ

@@

In most data mining and machine learning algorithms, the values of
some parameters have a high influence on its performance. In our
experiments, the best value of $k$ in the $k$-nearest neighbour was
empirically found at $k=3$. % What???? - JJ
 For SVM, the widely used Radial Basis
Function (RBF) kernel is selected. As reported in several studies, RBF
kernel has a reliable performance and can analyse higher dimensional
data \cite{yu2004ec,chao2015construction,huang2006ga}. Two important
parameters should be tuned in SVM: the Cost $(C)$ and $(\gamma)$ of
the RBF kernel. We apply grid search which is the most common approach
to find $C$ and $\gamma$. The best performance of SVM was found at
$C=200$ and Gamma $\gamma = 0.01$. For MLP, we apply it with one
hidden layer since it was proven in the literature that an MLP with
one hidden layer can approximate any continuous or discontinuous
function \cite{hornik1989multilayer,mirjalili2014let}. However, there
is no rule of thumb on selecting the best number of neurons in the
hidden layer. One suggested method that is followed in this work is to
set the number of neurons in the hidden layer to $2 \times I + 1$
where $I$ is the number of inputs in the dataset
\cite{wdaa2008differential,mirjalili2014let,mirjalili2015effective}.

All experiments are performed using 10-fold cross validation. The
dataset is partitioned into 10 parts where the training process is
carried out on 9 parts then the resulted model is tested on the left
10th part. This process is repeated 10 times, each time the model is
trained using different 9 parts. At the end of the process the 10
evaluation results on the testing parts are averaged.

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.60]{freq_sales.eps}
\end{center}
\caption{Number of books in each category.}
%This should go also to exploratory data analysis, that is, problem
%description - JJ
\label{fig:count}
\end{figure*}

@@

In Figure \ref{fig:Umatrix} we label the U-matrix with the total-sales
categories. It can be clearly seen that the SOM algorithm has
successfully clustered the labels of the Total Sales into clear
identified regions. %So what? - JJ
 In the top of the U-matrix the VL category is
located. The L category appears in the middle of the matrix. Most of
the M category appears in bottom-right corner while the H and VH
categories are concentrated in the bottom-left corner.
% OK, this means that these features are more or less clearly
% separable. But the problem is that the UMatrix shows only 2, maybe 3
% clusters: vh and H. That's it. If you know UMatrix, that's what you
% see - JJ
By inspecting \texttt{num\_reprints}, \texttt{gifts},
\texttt{distrib\_novelty}, \texttt{tot\_points\_sale},
\texttt{tot\_points\_sale\_1st\_year} and \texttt{print\_run}
components, it can be noticed that they have the highest similarity to
the clusters shown in the U-matrix. Based on this analysis, those
features will be selected for the next stage.
%  This is not a result, it is data preprocessing. You should have
%  included it in the 4th section. All results do not need to go into
%  the "REsults" section, only the final results. 
% Besides, are you using this or feature selection for selecting
% features?

@@

\begin{figure*}[http] 
\begin{center} 
\begin{tabular}{ccc}
\includegraphics[scale=0.22]{m5p.eps}  &
\includegraphics[scale=0.22]{lr.eps}   &
\includegraphics[scale=0.22]{svm.eps}  \\
M5P & LR & SVM 
\end{tabular}
\begin{tabular}{cc}
\includegraphics[scale=0.22]{knn.eps}  &
\includegraphics[scale=0.22]{mlp.eps}  \\
k-NN & MLP
\end{tabular}
\end{center} 
\caption{Actual vs. predicted sales for M5P, LR, SVM, k-NN, MLP
  models.}
% You should use a log-log scale here to see it more clearly. Besides,
% please say in a comment the script you are using to generate it, we
% are going to need it later on - JJ
\label{conv2}
\end{figure*}
